### 2024-06-11 doc/sections/mav-semantics.tex
[ tex ] NBE reference

To prove the normalisation property for all MAV proofs, we use a
semantic technique that is akin to Okada's phase space method and to
Normalisation by Evaluation (NbE). We construct a semantics of the
whole proof system from the system of normal proofs. This semantics is
constructed in such a way that after interpreting a proof, the
(existence of) a normal form can be extracted (or \emph{read back} or
\emph{reified} in NbE terminology) from the semantic proof.

>>>>

To prove the normalisation property for all MAV proofs, we use a
semantic technique that is akin to Okada's phase space method and to
Normalisation by Evaluation (NbE) \cite{BergerES98}. We construct a semantics of the
whole proof system from the system of normal proofs. This semantics is
constructed in such a way that after interpreting a proof, the
(existence of) a normal form can be extracted (or \emph{read back} or
\emph{reified} in NbE terminology) from the semantic proof.
